\documentclass{mimosis}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsfonts}
\usepackage[toc,page]{appendix}
\usepackage{bm}
\usepackage{chngcntr}
\usepackage[ngerman,english]{cleveref}
\usepackage{environ}
\usepackage{numprint}
\usepackage[super]{nth}
\usepackage{placeins}
\usepackage{svg}
\usepackage{tikz}
\usepackage[textsize=footnotesize]{todonotes}

\usetikzlibrary{arrows, arrows.meta, calc, decorations.pathreplacing, patterns,
positioning}

%%% Cleveref settings %%%
\Crefname{equation}{Eq.}{Eqs.}
\newcommand{\crefrangeconjunction}{--}
\AtBeginEnvironment{appendices}{
\crefalias{section}{appendix}
\crefalias{Section}{Appendix}
\crefalias{chapter}{appendix}
\crefalias{Chapter}{Appendix}
}

%%% Numprint settings %%%
\npthousandsep{,}%
\npdecimalsign{.}%
\npproductsign{\cdot}%
\npunitseparator{\,}%
\npdegreeseparator{}%
\npcelsiusseparator{\nprt@unitsep}%
\nppercentseparator{\nprt@unitsep}%

% shorter minus sign in \numprint exponents
\expandafter\renewcommand\csname nprt@sign@-\endcsname{%
\ifmmode {-}\else {\text{-}}\fi}

%%% Hyphenation %%%
\hyphenation{Page-Rank net-works}

% Avoid resetting footnotes after each part/chapter
%\makeatletter
%\pretocmd{\@schapter}{\setcounter{footnote}{0}}{}{}
\counterwithout*{footnote}{chapter}
%\pretocmd{\@chapter}{\setcounter{footnote}{0}}{}{}
%\makeatother

%%% Macros %%%
\input{sources/macros.tex}
\input{sources/thesis-macros.tex}

%%% Color changes for final version in blue %%%
\changesfalse

%%% Generated macros %%%
\input{sources/gen-macros/preliminaries.tex}
\input{sources/gen-macros/betweenness-approximation.tex}
\input{sources/gen-macros/dyn-topk.tex}
\input{sources/gen-macros/group-closeness-ls.tex}
\input{sources/gen-macros/group-closeness-harmonic.tex}
\input{sources/gen-macros/ged-walk.tex}
\input{sources/gen-macros/ged-harmonic.tex}
\input{sources/gen-macros/el-clos.tex}
\input{sources/gen-macros/forest-closeness.tex}
\input{sources/gen-macros/dyn-mwm.tex}
\input{sources/gen-macros/rw-macros.tex}

\input{sources/bibliography-mimosis}
\addbibresource{references.bib}

\input{sources/acronyms}
\input{sources/glossary}

\makeindex
\makeglossaries

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Incipit
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{\textbf{Scalable Algorithms for the Analysis of Massive Networks}}
\author{\textbf{Eugenio Angriman}}
\HUpresident{Prof. Dr.-Ing. Dr. Sabine Kunst}
\HUdean{Prof. Dr. Elmar Kulke}
\firstReviewer{Prof. Dr Henning Meyerhenke}
\secondReviewer{Prof. Dr. Giuseppe Francesco Italiano}
\thirdReviewer{Prof. Dr. Ulrik Brandes}
\date{14 Dezember 2021}


\begin{document}

\frontmatter
\include{sources/title}
\include{sources/decl-independent-work}
\cleardoublepage
\include{sources/acknowledgments}

\cleardoublepage
\include{sources/zusammenfassung}
\cleardoublepage
\include{sources/abstract}

\cleardoublepage
\tableofcontents
\vfill
\pagebreak
\listoffigures
\vfill
\pagebreak
\listoftables
\vfill
\pagebreak

\mainmatter

\part{Introduction}
\include{sources/1_introduction.tex}
\include{sources/2_preliminaries.tex}
\part{Algorithms for Single-Vertex Centrality Measures}
\label{part:single-vertex-centrality}
\include{sources/intro-part-2.tex}
\include{sources/3_dyn-top-closeness.tex}
\include{sources/4_betweenness-approximation.tex}
\include{sources/5_electrical-closeness.tex}
\part{Algorithms for Group Centrality Measures}
\label{part:group-centrality}
\include{sources/intro-part-3.tex}
\include{sources/6_group-closeness-local-search-heu.tex}
\include{sources/7_group-closeness-harmonic-approx.tex}
\include{sources/8_ged-walk.tex}
\part{Maximum Weighted Matching in Fully-Dynamic Graphs}
\label{part:matching}
\include{sources/intro-part-4.tex}
\include{sources/9_dyn-mwm.tex}
\part{Conclusion}
\label{part:conclusion}
\include{sources/conclusions}

%%% Appendices %%%
\begin{appendices}
\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}
\input{sources/appendix-publications.tex}
\input{sources/appendix-dyn-topk.tex}
\input{sources/appendix-betweenness-approximation.tex}
\input{sources/appendix-electrical-closeness.tex}
\input{sources/appendix-group-closeness-local-search.tex}
\input{sources/appendix-group-harmonic-closeness-maximization.tex}
\input{sources/appendix-ged-walk.tex}
\input{sources/appendix-dyn-mwm.tex}
\end{appendices}

% This ensures that the subsequent sections are being included as root
% items in the bookmark structure of your PDF reader.
%\bookmarksetup{startatroot}
\backmatter
%      \printacronymsandglossary
\begingroup
    \let\clearpage\relax
    \glsaddall
    \printglossary[type=\acronymtype]
    \newpage
    \printglossary
\endgroup
\printindex
\printbibliography

\end{document}
