\pagestyle{plain}
\begin{center}
  \textsc{Acknowledgments}
\end{center}
%
\noindent
%
I want to dedicate a few words to everyone who helped me write this thesis.

First and foremost, my supervisor Henning Meyerhenke: he offered me the
opportunity to work in his research group and, even in rough times, was never
too busy to provide support and guidance during my PhD. I also appreciate his
trust, his efforts in keeping the group united and collaborative, and for the
time he spent to give me valuable advice.
I would also like to thank Giuseppe Francesco (Pino) Italiano and
Ulrik Brandes for accepting to act as reviewers of my thesis and taking the time
to read it as well as Jan Mendling, Robert Bredereck, and Patrick Schäfer for
agreeing to be part of the PhD committee.

A great thank you goes to past and present colleagues I was fortunate to
work with. In particular, Elisabetta Bergamini: even though we just exchanged
a few emails about NetworKit while I was working on my Master's thesis,
her enthusiasm in her work encouraged me to join Henning's group.
Also, thank you for the great tips about life in Germany!
I am very grateful to Charilaos (Harry) Tzovas for his hospitality during
my first days in Karlsruhe, for helping when we moved to Berlin, and for
his contagious good mood.
Thank you also to Moritz von Looz for helping me since the beginning of my PhD,
for the intriguing discussions and the board game evenings.
Thanks to Roland Glantz for your help during my months in Karlsruhe and for
lending me a nice white shirt which made me look (slightly) more professional
during the group photo day -- which I forgot about.
I also thank Maria Predari, the most competitive foosball player I have ever met
-- too bad that we did not buy a foosball table after we moved to Berlin, but
it probably would have made us miss a few deadlines.
A special thank you goes to Alexander van der Grinten for the time he spent listening
to my questions and for his guidance that made me a better researcher and programmer.
My gratitude also goes to Fabian Brandt-Tumescheit for always being available to
solve any kind of technical issues (for some of which I am directly responsible),
for the great support he gave us to carry on and promote our research work, and for
helping me translate the abstract of this thesis together with Alexander.
% Klaus

I wish to thank all my coauthors and collaborators enjoyed working with: Martin
N\"ollenburg, Aleksandar Bojchevski, Daniel Z\"ugner, Stephan G\"unnemann,
Christian Schulz, Bora Uçar, Ruben Becker, Gianlorenzo D'Angelo, Hugo Gilbert,
Klaus Ahrens, and Micha{\l} Boro{\'n}.
Thank you to all my colleagues from the DFG SPP project \enquote{Algorithms for
BIG DATA}, in particular, Michael Hamann, Manuel Penschuck, Timo Bingmann,
Demian Hespe, Lorenz Hübschle-Schneider. Thank you for the interesting
discussions and the fun we had at conferences around Germany and in India.

I am also thankful to my friends Davide, Giuseppe, Gianluca, Emanuele, Massimo,
Giacomo, Elia, Stefano, Federico, and Nicola for being there. I am glad that,
despite many of us are living abroad, we still manage to see each other and
have fun together.
%
For their great support, I thank my parents Cecilia and Imerio, my
parents-in-law Katya and Alberto, my siblings Sofia and Daniele, and my
siblings-in-law Davide and Arianna.

Last but not least, I cannot describe in words my gratitude to my girlfriend Francesca.
Since the beginning of this journey, you always supported me with your love,
patience, and joy.
Despite the distance that separated us during these years, you have always been there for me.
Thank you.
